---
title: "Selecting ETFs for each asset class"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Part 1 determined which lazy portfolios were the best performers.  Part 2 will determine which ETFs are the best choices for these lazy portfolios.  The selection basis will be contingent on the expense ratio and their alpha.    

356 stock instruments across 10 asset classes were hand scraped from ETFdb.com.  The following is a jitter overlaid by a box and whisker of the expense ratios of each ETF separating according to asset class.  It's definitely a busy graph, but it provides an unadulterated view of the entire data set.  Let's dive deeper.  


```{r load, echo=FALSE}
setwd("/Volumes/DATA/Github/LazyPortfolioAnalytics")
#

# Load libraries
library(readxl)
library(rPref)  # for psel
library(ggplot2)
library(scales)  # for percent
library(ggrepel)  # for geom_text_repel
library(gridExtra) # for grid.arrange

# Load list of ETFs
df <- data.frame(read_excel("etfdb_data.xls"))
colnames(df) = c("symbol","name","etfdb.category","inception.date","expense.ratio","commission.free","expenses.rating")
# Correct Excel format date for inception date
df$inception.date = as.Date(df$inception.date,origin = "1899-12-30")
df["c.issuer"] = gsub( " .*$", "", df$name )

n.top = 10

df.ac = psel(subset(df,etfdb.category == "All Cap Equities"),low(expense.ratio),top = n.top)
df.lcb = psel(subset(df,etfdb.category == "Large Cap Blend Equities"),low(expense.ratio),top = n.top)
df.lcg = psel(subset(df,etfdb.category == "Large Cap Growth Equities"),low(expense.ratio),top = n.top)
df.lcv = psel(subset(df,etfdb.category == "Large Cap Value Equities"),low(expense.ratio),top = n.top)
df.mcb = psel(subset(df,etfdb.category == "Mid Cap Blend Equities"),low(expense.ratio),top = n.top)
df.mcg = psel(subset(df,etfdb.category == "Mid Cap Growth Equities"),low(expense.ratio),top = n.top)
df.mcv = psel(subset(df,etfdb.category == "Mid Cap Value Equities"),low(expense.ratio),top = n.top)
df.scb = psel(subset(df,etfdb.category == "Small Cap Blend Equities"),low(expense.ratio),top = n.top)
df.scg = psel(subset(df,etfdb.category == "Small Cap Growth Equities"),low(expense.ratio),top = n.top)
df.scv = psel(subset(df,etfdb.category == "Small Cap Value Equities"),low(expense.ratio),top = n.top)

```


## Including Code

You can include R code in the document as follows:

```{r plot.code, echo=FALSE}
# Plot box-whisker for each category

plot.box = ggplot(df,aes(x = etfdb.category,y = expense.ratio)) + 
  geom_boxplot(outlier.colour = "black", outlier.size = ) +
  geom_jitter(aes(colour = etfdb.category)) + 
  scale_y_continuous(labels = percent,breaks = scales::pretty_breaks(n = 10)) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))  


plot.lcb = ggplot() + 
  geom_point(data = df.lcb,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.lcb,aes(x = c.issuer,y = expense.ratio,label = df.lcb$symbol)) + 
  ggtitle("Large Cap Blend") +
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

plot.lcg = ggplot() + 
  geom_point(data = df.lcg,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.lcg,aes(x = c.issuer,y = expense.ratio,label = df.lcg$symbol)) + 
  ggtitle("Large Cap Growth") +
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

plot.lcv = ggplot() + 
  geom_point(data = df.lcv,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.lcv,aes(x = c.issuer,y = expense.ratio,label = df.lcv$symbol)) + 
  ggtitle("Large Cap Value") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

plot.mcb = ggplot() + 
  geom_point(data = df.mcb,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.mcb,aes(x = c.issuer,y = expense.ratio,label = df.mcb$symbol)) + 
  ggtitle("Small Cap Blend") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

plot.mcg = ggplot() + 
  geom_point(data = df.mcg,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.mcg,aes(x = c.issuer,y = expense.ratio,label = df.mcg$symbol)) + 
  ggtitle("Mid Cap Growth") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

plot.mcv = ggplot() + 
  geom_point(data = df.mcv,aes(x = c.issuer,y = expense.ratio)) +
  geom_text_repel(data = df.mcv,aes(x = c.issuer,y = expense.ratio,label = df.mcv$symbol)) + 
  ggtitle("Mid Cap Value") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

  
plot.scb = ggplot() + 
  geom_point(data = df.scb,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.scb,aes(x = c.issuer,y = expense.ratio,label = df.scb$symbol)) + 
  ggtitle("Small Cap Blend") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
  
  
plot.scg = ggplot() + 
  geom_point(data = df.scg,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.scg,aes(x = c.issuer,y = expense.ratio,label = df.scg$symbol)) + 
  ggtitle("Small Cap Growth") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))

plot.scv = ggplot() + 
  geom_point(data = df.scv,aes(x = c.issuer,y = expense.ratio)) + 
  geom_text_repel(data = df.scv,aes(x = c.issuer,y = expense.ratio,label = df.scv$symbol)) + 
  ggtitle("Small Cap Value") + 
  scale_y_continuous(labels = percent) + 
  theme(legend.title=element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))


```

## Including Plots

You can also embed plots, for example:

```{r plot, fig.width = 11, fig.height = 11, echo=FALSE}
plot.box
grid.arrange(plot.lcv,plot.lcb,plot.lcg,plot.mcv,plot.mcb,plot.mcg,plot.scv,plot.scb,plot.scg,ncol = 3)
```
